A Framework for Substructural Type Systems \thanks{Supported by organization x.}

### 2021-10-15 tex/esop22/syntax.tex
[ writing ] cut Section 4 into paragraphs

\subsection{A prototypical type system}

\subsection{Descriptions}

We capture the form of rules exemplified previously\todo{Previously?} via
\emph{descriptions} of rules.
The key to making these descriptions work is that they only allow syntactic
forms that preserve environments.
These forms are: absence and multiplicity of subterms with the same usage
annotations, absence and multiplicity of subterms with summed usage annotations,
scaling of a subterm, and variable binding.

@@

@@

@@

A layer of syntax supports the following functorial action.

\ExecuteMetaData[\Maptex]{map-s-type}

>>>>

We capture the form of rules exemplified previously\todo{Previously?} via
\emph{descriptions} of rules.
The key to making these descriptions work is that they only allow syntactic
forms that preserve environments.
These forms are: absence and multiplicity of subterms with the same usage
annotations, absence and multiplicity of subterms with summed usage annotations,
scaling of a subterm, and variable binding.\todo{Switching to Agda}

\paragraph{Premises, Rules, and Systems.}

@@

\paragraph{\figref{fig:lr-comb} as a \AgdaRecord{System}.}

@@

\paragraph{Terms of a \AgdaRecord{System}.}

@@

% A layer of syntax supports the following functorial action.

% \ExecuteMetaData[\Maptex]{map-s-type}
